Energy Regulation for Biologically-inspired Robotics

### 2021-09-17 latex/nserc/contributions.tex
First draft of the contributions document

\subsection*{Part III: Applicant's Statement}
\subsubsection*{Research Experience}
\textit{Describe scientific and engineering abilities you gained in past
    research experience, including projects, honours thesis, coop reports. If
    you have work experience, discuss relevance of that to your proposed field
of study and what benefits you gained.}
The following list outlines the scientific and engineering abilities I gained in
my research and professional roles.
\begin{itemize}
    \item \textbf{MASc Research, University of Toronto, 2018 -- 2021}
        TODO.
        Research skills: time management, critical thinking, coming up with
        well-formulated research question, tenacity and creativity
        (always ``attacking" the problem from multiple directions), dedication
        to solving a complex problem, explaining
        my work both orally and in writing, presentation skills, 
        literature reviews and how to read papers
        Engineering skills: nonlinear control techniques, implementation of
        control systems on hardware

    \item \textbf{Radar Developer, 2018}
        TODO:
        Managing a software project, implementing software for a hardware
        system, validating documentation (i.e. never trust it blindly).

    \item \textbf{Undergraduate Thesis, Queen's University, 2017 -- 2018}
        TODO:
        First time doing a research project. Collaborating with fellow
        researchers. Coming up with an application for existing research. Basic
        literature review skills, report writing. Code optimization (turning
        equations into matrix form for speed, parallelization, C++ vs MATLAB),
        creating a GUI for users.

>>>>

\subsection*{Part III: Applicant's Statement}
\subsubsection*{Research Experience}
\textit{Describe scientific and engineering abilities you gained in past
    research experience, including projects, honours thesis, coop reports. If
    you have work experience, discuss relevance of that to your proposed field
of study and what benefits you gained.}
The following list outlines the scientific and engineering abilities I gained in
my research and professional roles.
\begin{itemize}
    \item \textbf{MASc Research, University of Toronto, 2018 -- 2021}
        In my master's degree, I learned several important research skills.
        My supervisor taught me to formulate research questions
        correctly; I learned the tenacity and dedication required to solve a
        complex problem; I found creative solutions by attacked problems from
        multiple directions; I learned to read papers, perform a literature
        review, think critically about the literature, and to apply existing
        results to my research; I improved my time management skills, practiced
        explaining my work (both orally and in writing), and improved my
        presentation skills for the thesis defense. Finally, I learned to write
        research papers and a thesis, which is important for communicating my
        work to the engineering community.
        I also learned several engineering skills, including: advanced control
        techniques; simulating physical systems in MATLAB; and implementing
        control systems in hardware.

    \item \textbf{Radar Developer, University of Toronto, 2018}
        As part of a course project, I learned useful engineering skills by
        writing software for a radar device.
        First, I improved my project management skills by keeping our group
        meetings organized, and by separating the tasks in such a way
        that everyone was learning something from the project.
        I learned to read hardware documentation; to program a hardware
        device by implementing the documentation in software;
        and to validate the claims of the hardware capabilities for myself,
        i.e., to never blindly trust documentation.

    \item \textbf{Undergraduate Thesis, Queen's University, 2017 -- 2018}
        My undergraduate thesis was my first time doing a research project.
        I learned to do collaborative application-based research; that is, I
        worked with my peers to find an application for existing theoretical
        results. During this project I also learned to perform a basic
        literature review, and to manage deadlines with a supervisor.
        In terms of engineering skills, I learned to write reports in LaTeX,
        and my thesis group worked together on code optimization. We learned to
        convert equations into matrix form to make use of hardware speed; we
        parallelized our code to take advantage of multithreading; we ported
        MATLAB code to C++ to achieve faster algorithms; and we created a GUI so
        we could test our code quickly and easily.
